---
title: "Correlation"
author: "Noor Pratap Singh"
date: "12/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/fs/cbcb-lab/rob/students/noor/shoal_proj/')
```

```{r}
suppressPackageStartupMessages(source("run_limma.R"))
dirSal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/sal_best/vbprior=1e0"
```

##### Correlation between Salmon and Shoal for weight 1e-05 for fixed prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_fixed_prior/vbprior=1e0/c=1e-05"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```

##### Correlation between Salmon and Shoal for weight 100 for fixed prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_fixed_prior/vbprior=1e0/c=100"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```

##### Correlation between Salmon and Shoal for weight 1e-05 for old prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best/vbprior=1e0/c=1e-05"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```

##### Correlation between Salmon and Shoal for weight 100 for old prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best/vbprior=1e0/c=100"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```

##### Correlation between Salmon and Shoal for weight 0.1 for updated prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=0.1"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```


##### Correlation between Salmon and Shoal for weight 1e-05 for updated prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=1e-05"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```

##### Correlation between Salmon and Shoal for weight 100 for updated prior
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=100"
dfSal <- getQuantFiles(dirSal, type="salmon")
dfShoal <- getQuantFiles(dirShoal, type="shoal")

txiSal <- tximport(dfSal[["files"]], type="salmon", txOut=T)
txiShoal <- tximport(dfShoal[["files"]], type="salmon", txOut=T)

corr <- sapply(seq(12), function(i) cor(txiSal[["counts"]][,i], txiShoal[["counts"]][,i], method = "spearman"))
print(corr)
```