---
title: "Differential Analysis"
author: "Noor Pratap Singh"
date: "12/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/fs/cbcb-lab/rob/students/noor/shoal_proj/')
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
suppressPackageStartupMessages(source("run_limma.R"))
dirSal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/sal_best/vbprior=1e0"
load("/fs/cbcb-lab/rob/students/noor/Uncertainity/mikelove-swimdown-216a1dd/simulate/data/simulate.rda")
```

### Doing differential analysis on old shoal
#### Weight 0.00001
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best/vbprior=1e0/c=1e-05"
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 100 aka optimal
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best/vbprior=1e0/c=100"
runDE(dirSal, dirShoal)
```

#### Weight 100000 (large)
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best/vbprior=1e0/c=100000"
suppressWarnings(runDE(dirSal, dirShoal))
```

### Doing differential analysis on shoal with fixed prior
#### Weight 0.00001
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_fixed_prior/vbprior=1e0/c=1e-05"
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 100 aka optimal
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_fixed_prior/vbprior=1e0/c=100"
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 100000
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_fixed_prior/vbprior=1e0/c=100000"
suppressWarnings(runDE(dirSal, dirShoal))
```

### Doing differential analysis on updated shoal (Requant v2)
#### Weight 0
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=0"
suppressWarnings(runDE(dirSal, dirShoal))
```
#### Weight 0.00001
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=1e-05"
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 0.1 (Optimal)
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=0.1"
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 100000 (large)
```{r}
dirShoal <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_updated/vbprior=1e0/c=100000"
suppressWarnings(runDE(dirSal, dirShoal))
```

### Doing differential analysis on shoal where factor has been set to 1 (Requant v2)
#### Weight 0
```{r}
dir <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_uni_fac/vbprior=1e0/"
dirShoal <- file.path(dir, "c=0")
suppressWarnings(runDE(dirSal, dirShoal))
```
#### Weight 0.00001
```{r}
dirShoal <- file.path(dir, "c=1e-05")
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 0.1 (Optimal)
```{r}
dirShoal <- file.path(dir, "c=0.1")
suppressWarnings(runDE(dirSal, dirShoal))
```

#### Weight 100000 (large)
```{r}
dirShoal <- file.path(dir, "c=100000")
suppressWarnings(runDE(dirSal, dirShoal))
```

### Doing differential analysis on (Requant v2) with factor set based on true de status
#### Weight 0.1
```{r}
dir <- "/fs/cbcb-lab/rob/students/noor/shoal_proj/swim/shoal_best_true_de_fac/vbprior=1e0/"
dirShoal <- file.path(dir, "c=0.1")
suppressWarnings(ddS <- runDE(dirSal, dirShoal))
```